---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Amalie Lysgaard Andersen"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/4. Aarhus Universitet/3. Semester/1. Experimental Methods lll/R FOLDER/Heart rate/Heart rate")    
 
locpath <- setwd("~/Library/Mobile Documents/com~apple~CloudDocs/4. Aarhus Universitet/3. Semester/1. Experimental Methods lll/R FOLDER/Heart rate/Heart rate")  

library(pacman)
p_load(lmerTest, pastecs, ggplot2, tidyverse, gdata, MuMIn, effects, stringr, plyr, Metrics, vtreat, cvTools, simr,stringi, e1071, caret,sjPlot, boot, zoo, gridExtra)

### packages needed for crqa analysis
# library(crqa)
#library(ggplot2)
library(reshape2)
library(tseriesChaos)
library(gridExtra) 
library(crqa)

 
# from class
#zoo::ina.spline 

```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
```{r Loading}
# Loading group 1 
conv <- read.csv("Study3_G1_T3_Conversation.csv")
turn <- read.csv("Study3_G1_T2_TurnTaking.csv")
sync <- read.csv("Study3_G1_T1_Synchronous.csv")

# Changing variable names
conv <- rename.vars(conv,"TimeMs", "time")
turn <- rename.vars(turn,"TimeMs", "time")
sync <- rename.vars(sync,"TimeMs", "time")
```

- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)

```{r First plots}
### Respiration plot 
#conv
ggplot(conv, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Respiration", title="Respiration as a function of time (Conversation)") +
  theme(legend.position ="none")

#sync
ggplot(sync, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Respiration", title ="Respiration as a function of time (Sync)") +
  theme(legend.position ="none")

#turn 
ggplot(turn, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Greedy", title ="Respiration as a function of time (turn-taking)") +
  theme(legend.position ="none")


### HR plot
#conv
ggplot(conv, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (turn-taking)") +
  theme(legend.position ="none")
 
#sync
ggplot(sync, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (sync)") +
  theme(legend.position ="none")

#turn
ggplot(turn, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (turn-taking)") +
  theme(legend.position ="none")


```

### Preprocessing
```{r Downsampling}
## Downsampling first   
p_load(groupdata2) 

turn_1 = turn %>% 
  group(n = 100, method = 'greedy') %>% 
  dplyr::summarise(time = mean(time,na.rm=T), 
                   HR1 = mean(HR1,na.rm=T),  
                   HR2 = mean(HR2,na.rm=T), 
                   Resp1 = mean(Resp1,na.rm=T),  
                   Resp2 = mean(Resp2,na.rm=T))

sync_1 = sync %>%
  group(n = 100, method = 'greedy') %>% 
  dplyr::summarise(time = mean(time,na.rm=T), 
                   HR1 = mean(HR1,na.rm=T), 
                   HR2 = mean(HR2,na.rm=T), 
                   Resp1 = mean(Resp1,na.rm=T), 
                   Resp2 = mean(Resp2,na.rm=T))

conv_1 = conv %>%
  group(n = 100, method = 'greedy') %>% 
  dplyr::summarise(time = mean(time,na.rm=T), 
                   HR1 = mean(HR1,na.rm=T), 
                   HR2 = mean(HR2,na.rm=T), 
                   Resp1 = mean(Resp1,na.rm=T), 
                   Resp2 = mean(Resp2,na.rm=T))

# Group by chunks of 100 and take mean time etc of each group
```

```{r Rescaling}
### HR 
# Conversation
conv_1$HR1 <- scale(conv_1$HR1)
conv_1$HR2 <- scale(conv_1$HR2)

# Sync
sync_1$HR1 <- scale(sync_1$HR1)
sync_1$HR2 <- scale(sync_1$HR2)

# Turn
turn_1$HR1 <- scale(turn_1$HR1)
turn_1$HR2 <- scale(turn_1$HR2)



### Respiration
# Conversation
conv_1$Resp1 <- scale(conv_1$Resp1)
conv_1$Resp2 <- scale(conv_1$Resp2)

# Sync
sync_1$Resp1 <- scale(sync_1$Resp1)
sync_1$Resp2 <- scale(sync_1$Resp2)

# Turn
turn_1$Resp1 <- scale(turn_1$Resp1)
turn_1$Resp2 <- scale(turn_1$Resp2)

```

```{r Plots preprocessed}
### Respiration plot 
#conv
ggplot(conv_1, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Respiration", title="Respiration as a function of time (Conversation)") +
  theme(legend.position ="none")

#sync
ggplot(sync_1, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Respiration", title ="Respiration as a function of time (Sync)") +
  theme(legend.position ="none")

#turn 
ggplot(turn_1, aes(time, Resp1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, Resp2), colour = "dark grey") +
  labs(x ="Time", y = "Greedy", title ="Respiration as a function of time (turn-taking)") +
  theme(legend.position ="none")


### HR plot
#conv
ggplot(conv_1, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (conv)") +
  theme(legend.position ="none")
 
#sync
ggplot(sync_1, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (sync)") +
  theme(legend.position ="none")

#turn
ggplot(turn_1, aes(time, HR1)) +
  geom_line( colour = "red") +
  geom_line(aes(time, HR2), colour = "dark grey") +
  labs(x ="Time", y = "Heart rate", title ="Heart rate as a function of time (turn-taking)") +
  theme(legend.position ="none")

```

```{r Artifacts}
# Removing artifacts 

hr_threshold = 2.75 
resp_threshold = 2.5 

# Function
cillitbang <- function(ts,threshold) {  
  ts[ts > (mean(ts,na.rm=T) + 
             (threshold * sd(ts,na.rm=T))) |  
       ts < (mean(ts,na.rm=T) - 
               (threshold * sd(ts,na.rm=T)))] = mean(ts,na.rm=T) 
  return(ts) 
  }  

    ### HEART RATE
# Conv
conv_1$HR1 <- cillitbang(conv_1$HR1,hr_threshold)
conv_1$HR2 <- cillitbang(conv_1$HR2,hr_threshold)

# Sync
sync_1$HR1 <- cillitbang(sync_1$HR1,hr_threshold)
sync_1$HR2 <- cillitbang(sync_1$HR2,hr_threshold)

#Turn
turn_1$HR1 <- cillitbang(turn_1$HR1,hr_threshold)
turn_1$HR2 <- cillitbang(turn_1$HR2,hr_threshold)

    ### RESPIRATION
# Conv
conv_1$Resp1 <- cillitbang(conv_1$Resp1, resp_threshold )
conv_1$Resp2 <- cillitbang(conv_1$Resp2,resp_threshold )

# Sync
sync_1$Resp1 <- cillitbang(sync_1$Resp1,resp_threshold )
sync_1$Resp2 <- cillitbang(sync_1$Resp2,resp_threshold )

#Turn
turn_1$Resp1 <- cillitbang(turn_1$Resp1,resp_threshold)
turn_1$Resp2 <- cillitbang(turn_1$Resp2,resp_threshold)
```

- Can you eye-ball which condition if any displays more physiological coordination?
Answer: HR for sync is somewhat coordinated. 

### Running CRQA

- Run crqa on heart rate and respiration data (find parameters, run crqa)
```{r crqa}
# Finding the optimal parameters: run on all pairs:

#lgM = Maximum lag
#radius span = 2?     increasing radius step means smaller steps
#radius sample = 10?  number of radius points within the steps to be sampled
# min diagline: minimum length of diagonal lines
par = list(lgM = 50, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 40, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline =FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip") 
  

# Respiration optimisation of parameters
par_conv_resp = optimizeParam(na.omit(conv_1$Resp1), na.omit(conv_1$Resp2), par, min.rec = 2, max.rec = 5)
par_conv_resp
par_turn_resp = optimizeParam(na.omit(turn_1$Resp1), na.omit(turn_1$Resp2), par, min.rec = 2, max.rec = 5)
par_turn_resp
par_sync_resp = optimizeParam(na.omit(sync_1$Resp1), na.omit(sync_1$Resp2), par, min.rec = 2, max.rec = 5)
par_sync_resp

# HR optimisation of parameters
par_conv_hr = optimizeParam(na.omit(conv$HR1), na.omit(conv$HR2), par, min.rec = 3.5, max.rec = 4.5)
par_conv_hr
par_turn_hr = optimizeParam(na.omit(turn_1$HR1), na.omit(turn_1$HR2), par, min.rec = 3.5, max.rec = 4.5)
par_turn_hr
par_sync_hr = optimizeParam(na.omit(sync$HR1), na.omit(sync$HR2), par, min.rec = 3.5, max.rec = 4.5)
par_sync_hr


radius <- 0.2876967   # Radius ??? cutoff boundary that will determine if two points are recurrent or not
delay <-  25          # Delay ??? how many points to consider when looking for recurrence 
emddim <- 2           # Embedding Dimension ??? lag unit
  

# Choose a common value for delay, emb.dim and radius
Results=crqa (g7_conv_1$HR1, g7_conv_1$HR2, delay=delay, embed=emddim, radius=radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)

# Represent the plot:
RP=Results$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4")
image(RP, xlab = "", ylab = "", col = cols)

# Explore the lags of coordination:
Profile=drpdfromts(g7_conv_1$Resp1, g7_conv_1$Resp2, datatype = 'continuous', ws=50, radius=radius)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
maxlag = Profile$maxlag/1000
profile = Profile$profile*100
Prof=data.frame(profile)
Prof

# Final plot
ggplot(Prof, aes(timecourse, profile)) +
  geom_line() +
  geom_vline(xintercept = timecourse[maxlag], colour='red')
 
```

- Does this tell you more than just eyeballing the plots?


### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.

# DATA LOADING
Chunks:
1. files) create list of filenames
2. loading function) function to import and clean one csv file

- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

```{r Loop to plot and preprocess} 
 
p_load(gdata)  

#Function that downsamples, rescales and  removes outliers. 
#Then print plots for HR and respiration in one 
#Lastly, creates variables with optimal parameters for crqa.   
 
#Output = dataframe and prints plots

vanish = function(filename, graphs = T, bangbycillit = T){
  
  #load file as csv
  df = read_csv(filename) 
  
  df <- rename.vars(df, "TimeMs", "time")
  
  #Downsample 
  df = df %>%    
  group(n= 100, method= 'greedy') %>%    
  dplyr::summarise(time= mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T), HR2 = mean(HR2,na.rm=T), Resp1 =  mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T)) 
   
  #Rescale and create this in a new scaled variable
  df$Resp1=scale(df$Resp1)  
  df$Resp2=scale(df$Resp2)  
  df$HR1=scale(df$HR1) 
  df$HR2=scale(df$HR2)
  
  if(bangbycillit == T) {
    
  #Removing outliers using thresholds from before
  df$HR1=cillitbang(df$HR1,hr_threshold)
  df$HR2=cillitbang(df$HR2, hr_threshold)
  df$Resp1=cillitbang(df$Resp1, resp_threshold)
  df$Resp2=cillitbang(df$Resp2, resp_threshold)
  }
  
  #Adding columns with study identification
  df$study = str_extract(filename, "Study(\\d)") 
  df$group = str_extract(filename, "G(\\d+)")
  df$trial = str_extract(filename, "T(\\d)")
  
  #gsub  - {n}: matches exactly n times.
  # $: matches the end of the string.
  
  df$condition = gsub('.{4}$', '', strsplit(filename, "_")[[1]][4])
  df$filename = filename
  
  
  ##Calculating optimal parameters
    par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2, minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")
  
  #Parameters for HR data
  optparamHR = try(optimizeParam(df$HR1, df$HR2, par, min.rec = 2, max.rec = 5))
  
  #Using loop from before, if the optimize function succeeded, save the results to the dataframe - if not, put NAs 
   if (length(optparamHR) > 1) {
   
  #need to unlist the parameters otherwise they can't be used for later calculations (no idea why it makes them a list in the first place)

   df$optRadiusHR = optparamHR$radius
   df$optEmbdimHR = optparamHR$emddim
   df$optDelayHR = optparamHR$delay 
   
   } else {
  
   df$optRadiusHR = NA
   df$optEmbdimHR = NA
   df$optDelayHR = NA
   }
  
  #Now for respiration data
  optparamResp = try(optimizeParam(df$Resp1, df$Resp2, par, min.rec = 2, max.rec = 5))
 
  #if the optimize function succeeded, save the results to the dataframe - if not, put NAs 
  if (length(optparamResp) > 1) {
    
    df$optRadiusResp = optparamResp$radius
    df$optEmbdimResp = optparamResp$emddim
    df$optDelayResp = optparamResp$delay

    } else {
    
    df$optRadiusResp = NA
    df$optEmbdimResp = NA
    df$optDelayResp = NA
    }
  
 
  #Writing new csv file with the new columns
  name = str_extract(filename, '.*(?=\\.csv)') #removing .csv from filename
  name = paste(name, "preprocessed.csv", sep = '_')
  
  #creating new directing to put files in 
  dir.create("Preprocessed", showWarnings = FALSE) #stops warnings if folder already exists
  
  #writing file to the new folder
  write.csv(df, file.path("Preprocessed", name), row.names=FALSE)
  if(graphs == T) {
  
  #Making plots 
  HR = ggplot(df, aes(time, HR1)) + 
    geom_line() + 
    geom_line(aes(time, HR2, color = "red")) + 
    ggtitle(filename) +
    theme(legend.position = "none")
  Resp = ggplot(df, aes(time, Resp1)) + 
    geom_line() + 
    geom_line(aes(time, Resp2, color = "red")) + 
    ggtitle(filename) +
  
      theme(legend.position = "none")
  
  #Set plots together
  grid.arrange(HR, Resp)
  
  #With arrangeGrob we can save to variable and then to disk
  plots = arrangeGrob(HR, Resp)
  
  #Giving each plot individual names for each plot based on the filename
  plotname = str_extract(filename, '.*(?=\\.csv)') #removing .csv from filename
  plotname = paste(plotname, "PLOT.png", sep = '_')
  
  #creating a folder for the plots 
  dir.create("Plots", showWarnings = FALSE) #stops warnings if folder already exists
  
  #writing file to the new folder
  
  #ggsave(plotname, plot = plots (the arrangeGrob variables), path = "Plots/")
  ggsave(file=plotname, plots, path = "Plots/")
  }
  
  #Return df
  return(df)
}


#Trying out the function (with jomfrurejsen)
titanic = vanish("Study3_G1_T3_Conversation.csv")
titanic = bind_rows(titanic)

#Creating a list of all the files
files = list.files(path = locpath, pattern = "*.csv", full.names = F)

#Running all data in the beautiful function
all_preprocessed = lapply(files, vanish)
all_preprocessed = bind_rows(all_preprocessed) 
```

```{r Outlier}
newdata <- all_preprocessed
newdata <-newdata[!(newdata$condition=="Synchronous" & newdata$group=="G9"),] 
```

```{r Median optimal parametres}
#Using median (more robust to outliers)
#NB: note that delay is not allowed to be 0, then set it to 1! 
optradius_resp = median(newdata$optRadiusResp, na.rm = T) 
optemddim_resp = median(newdata$optEmbdimResp, na.rm = T)
optdelay_resp = median(newdata$optDelayResp, na.rm = T)

optradius_hr = median(newdata$optRadiusHR, na.rm = T)
#optradius_hr = 
optemddim_hr = median(newdata$optEmbdimHR, na.rm = T)
#optemddim_hr =
#optdelay_hr = median(newdata$optDelayHR, na.rm = T)
optdelay_hr = 5  
```


### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
      Compare means of the stats --> do it across conditions + one for each of the indexes

  1. First getting the data's recurrence measures
```{r Loop RR}
newdata <- newdata %>%
  mutate(group_trial = str_c(group, trial, sep = " "))

pairs <- unique(newdata$group_trial)

par = list(lgM = 50, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 40, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")

crqa_df_hr <- NULL
crqa_df_resp <- NULL

# Loop for HR
for (i in pairs){
  currentpair = filter(newdata, group_trial == i)
  Results=crqa(currentpair$HR1, currentpair$HR2, delay=optdelay_hr, embed=optemddim_hr, radius=optradius_hr, normalize=0 ,rescale=0 , mindiagline = 2 ,minvertline = 2)
  
  temp_df <- data_frame(group_trial = unique(currentpair$group_trial),study = unique(currentpair$study),group = unique(currentpair$group),trial = unique(currentpair$trial),condition = unique(currentpair$condition), RR = Results$RR, DET = Results$DET, NRLINE = Results$NRLINE, LMAX = Results$maxL, L = Results$L,ENTR = Results$ENTR, rENTR = Results$rENTR, LAM = Results$LAM, TT = Results$TT)
if (i == 1){
    crqa_df_hr <- temp_df
  } else {
    crqa_df_hr <- rbind(crqa_df_hr, temp_df)
  }
}


# Loop for Resp 
for (i in pairs){
  currentpair = filter(newdata, group_trial == i)
  Results=crqa(currentpair$Resp1, currentpair$Resp2, delay=optdelay_resp, embed=optemddim_resp, radius=optradius_resp, normalize=0 ,rescale=0 , mindiagline = 2 ,minvertline = 2)

  temp_df <- data_frame(group_trial = unique(currentpair$group_trial),study = unique(currentpair$study),group = unique(currentpair$group),trial = unique(currentpair$trial),condition = unique(currentpair$condition), RR = Results$RR, DET = Results$DET, NRLINE = Results$NRLINE, LMAX = Results$maxL, L = Results$L,ENTR = Results$ENTR, rENTR = Results$rENTR, LAM = Results$LAM, TT = Results$TT)
if (i == 1){
    crqa_df_resp <- temp_df
  } else {
    crqa_df_resp <- rbind(crqa_df_resp, temp_df)
  }
}


mean(crqa_df_hr$RR) # [1] 4.377326
mean(crqa_df_resp$RR) # [1] 4.13281

#median(crqa_df_hr$RR)
#median(crqa_df_resp$RR)

```
 
  2. Now getting the recurrence measures for the data in shuffled pairs
```{r Shuffled pairs loop}
newdata <- newdata %>%
  mutate(group_trial = str_c(group, trial, sep = " "))
 
pairs <- unique(newdata$group_trial) 

par = list(lgM = 50, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 40, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")

crqa_df_hr_shuf <- NULL
crqa_df_resp_shuf <- NULL

# Loop for HR
set.seed(13)
for (i in pairs){
  currentpair = filter(newdata, group_trial == i)
  Results=crqa(sample(currentpair$HR1), sample(currentpair$HR2), delay=optdelay_hr, embed=optemddim_hr, radius=optradius_hr, normalize=0 ,rescale=0 , mindiagline = 2 ,minvertline = 2)
  
  temp_df <- data_frame(group_trial = unique(currentpair$group_trial),study = unique(currentpair$study),group = unique(currentpair$group),trial = unique(currentpair$trial),condition = unique(currentpair$condition), RR = Results$RR, DET = Results$DET, NRLINE = Results$NRLINE, LMAX = Results$maxL, L = Results$L,ENTR = Results$ENTR, rENTR = Results$rENTR, LAM = Results$LAM, TT = Results$TT)
if (i == 1){
    crqa_df_hr_shuf <- temp_df
  } else {
    crqa_df_hr_shuf <- rbind(crqa_df_hr_shuf, temp_df)
  }
}


# Loop for Resp 
set.seed(13)
for (i in pairs){
  currentpair = filter(newdata, group_trial == i)
  Results=crqa(sample(currentpair$Resp1), sample(currentpair$Resp2), delay=optdelay_resp, embed=optemddim_resp, radius=optradius_resp, normalize=0 ,rescale=0 , mindiagline = 2 ,minvertline = 2)

  temp_df <- data_frame(group_trial = unique(currentpair$group_trial),study = unique(currentpair$study),group = unique(currentpair$group),trial = unique(currentpair$trial),condition = unique(currentpair$condition), RR = Results$RR, DET = Results$DET, NRLINE = Results$NRLINE, LMAX = Results$maxL, L = Results$L,ENTR = Results$ENTR, rENTR = Results$rENTR, LAM = Results$LAM, TT = Results$TT)
if (i == 1){
    crqa_df_resp_shuf <- temp_df
  } else {
    crqa_df_resp_shuf <- rbind(crqa_df_resp_shuf, temp_df)
  }
}


mean(crqa_df_hr_shuf$RR)    # [1] 0.004663804
mean(crqa_df_resp_shuf$RR)  # [1] 4.022755

#median(crqa_df_hr$RR)
#median(crqa_df_resp$RR) 
```

  3. Statistic comparison between the data and shuffled data 
```{r Stats - T-Test}
#### T-test for heart rate
t.test(crqa_df_hr$RR, crqa_df_hr_shuf$RR)

## Results
# t = 7.8317, df = 25, p-value = 3.454e-08
#alternative hypothesis: true difference in means is not equal to 0
#95 percent confidence interval:
# 3.222768 5.522557
#sample estimates:
#  mean of x   mean of y 
#4.377326239 0.004663804 


#### T-test for Respiration
t.test(crqa_df_resp$RR, crqa_df_resp_shuf$RR) 
## Results
# t = 0.48347, df = 48.644, p-value = 0.6309
#alternative hypothesis: true difference in means is not equal to 0
#95 percent confidence interval:
# -0.3474788  0.5675897
#sample estimates:
#mean of x mean of y 
# 4.132810  4.022755 
```


### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Malte will share a method to do this on screen.
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 
  1. First creating a function to extract rqa in the next sections loop
```{r Function: Extract rqa}
# Defining a function to extract rqa values 
rqa_extractor = function(t1, t2, embed, delay, radius){ #making a function which applied the optimal parameters and then saves the rqa results 
  result = try(crqa(t1, t2, embed = embed, delay = delay, radius = radius, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE)) 
  if (length(result) > 1){ 
    results_df = data.frame(RR = result[1], DET = result[2], NRLINE = result[3], maxL = result[4], L = result[5], ENTR = result[6], rENTR = result[7], LAM = result[8], TT = result[9]) 
  } 
  else { results_df = data.frame(RR = NA, DET = NA, NRLINE = NA, maxL = NA, L = NA, ENTR = NA, rENTR = NA, LAM = NA, TT = NA) 
  } 
  return(results_df) 
}
```

  2. Getting the recurrence measures for the data in surrogate pairs
```{r Surrogate pairs loop}
#Surrogate pairs (Kenneths kode)
i = 1 
all_dat = newdata

for (g in seq(unique(all_dat$group))){ #loop through all the groups 
  g1 = unique(all_dat$group)[g]
  non_g1 = unique(all_dat$group)[unique(all_dat$group)!= g1] #a list of groups which does not include g1
  g2 = sample(non_g1)[1] #randomly select a group which is in the non_g1 vector
  print(g1)

  for (c in unique(all_dat$condition)){ #looping through conditions 
    temp1 = subset(all_dat, group == g1 & condition == c) #e.g. the first group in condition 'turntaking
    temp2 = subset(all_dat, group == g2 & condition == c) #e.g. the second group in condition 'turntaking
      #doing rqa
    result_Resp = rqa_extractor(t1 = temp1$Resp1, t2 = temp2$Resp2, embed = optemddim_resp, 
                                delay = optdelay_resp, radius = optradius_resp)
    result_HR = rqa_extractor(t1 = temp1$HR1, t2 = temp2$HR2, embed = optemddim_hr, 
                              delay = optdelay_hr, radius = optradius_hr)
    colnames(result_Resp) = paste(colnames(result_Resp), "Resp", sep = ".")
    colnames(result_HR) = paste(colnames(result_HR), "HR", sep = ".")
    
    temp = cbind(result_Resp, result_HR)
    temp$condition = c
    temp$group1 = g1
    temp$group2 = g2
    if (i == 1){ #create df
      surPair_rqa = temp
      i = 2 #if you have already done this then don't do it again
    } else { #append to df
      surPair_rqa = rbind(surPair_rqa, temp)
    }
  print(c)
  }
}

# Output = surPair_Rqa dataframe with the different parametre values for each pair

```

  3. Statistic comparison between the data and surrogate pairs
```{r}
 
 
```



### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them




--- THE ASSIGNMENT ---
These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.


2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. Because of the timing, we're starting this exercise before collecting the data.
Instead, you will develop your script this week on data from two years ago (Study1) and last year (Study2).
When you hand in the assignment for feedback, you can use the old data. But when you hand in the final version for the exam, you need to adapt your script to use the data we collect next week in the lab.
(For the old data): Note that synchronouns and turn-taking are the same task across both studies, but the third condition is different: two years ago it was self-paced joint reading; last year it was tv-series conversation.

NB: For this exercise, you will need to do something very similiar to what you've done before spread over several weeks. Ie parse data, look at the plots, decide on data cleaning, build a model, and finally evaluate and interpret the results of the models. Going back and copying the approach from previous exercises will likely be a great help.


--- CLASS: Talkthrough --- 
#Preprocessing

1. Downsampling. 
- We have a lot of data --> DS done by taking means throughout the data
- We might introduce some noise, and miss information. 
- We should try to get as representative data as possible. 
- The variations we're interested in is how HR changes - this can be affected through downsampling. 

2. Artifacts (outliers). Problem with monitoring. 
How to detect?
- We need to figure out a threshold --> calculate a mean and SD and create a threshold based on those measurements, but also look at the plots to make sure no actual data should be cut off. Not a perfect way, but doable!
- Make one threshold for everyone (might cut off data, but must be scientifically rigorous) --> all data should be treated the same
- Make sure to make an informed decision based on the plots. 

3. Centering and scaling
- Third step in cleaning
- Rescaling: Both having a sd of 1 and a mean of 0

4. 
- Defining a threshold and everything that is outside of this and 1 sd of it should be set to the mean. 
- Setting to the mean has a consequence 
- One solution: not necessarily good to put in a mean interval, as we're interested in the development (which will be ruined by random data)
- Another: try to "draw a line", which keeps the overall structure but doesn't use mean+sd
- Malte: plot the timeseries! This will make clear the consequences of our actions

# Now recurrence quantification analysis

1. Recurrence plot
- Shows a dot (one participant on one axis, another on the other) if their data are recurring in time
- Important to run the whole analysis with the same threshold --> otherwise not comparable
- Once given parameters, the algorithm loops thorugh the whole plot
      - A line: If two timeseries are following each other and are synchronised. Can be across time. They are oftenmost the most                interesting. Many long lines: coordination between participants!
      - Diagonal lines are most interesting!
      - A box : If two timeseries are following each other in both time and with a small variability. The boxes could indicate errors           though

2. Measures/features to look for
- RR: Recurrence rate. The amount of the plot that is black. The absolute number will be meaningless, but interesting when             comparing
- L: The average length of the diagonal lines. The larger the L = the longer the line length = the longer stretches of coordination. An   L value of 2 indicate not a lot of coordination (this is the minimum value!)
- Lmax: Maximal length of the diagonal lines. 
- TT: Trapping time. Average lenght of the horizontal and vertical lines (they mean the same thing, but are difefrent participants        perfoming!). Refers to the squares
- DET: Determinism. The proportion of the all matches being part of a diagonal line. 
    - High DET = When the signals meet and do it for a while in a row 
    - Low DET = might be because the coordination is by chance

3. Hypotheses
- Sync: we expect more coordination bacuase they physically perform the same thing!
- Turn: not as much coordination as sync, but still expect some coord. We might expect more on the off-diagonal
- Note: Coordination can be captured in many ways!

4. Doing stats on the features in point 2
- Probability is always defined out of a distribition/group - what is the group in our case?

  Three different statisitical comparisons
  1. Compare across the different conditions/task. Is there a different coordination from conversations, turn-taking...
  2. Shuffled pairs: Randomising the order: what RQA measures do we get from a random distribution of numbers, losing the actual        progress of the HR etc
  3. Surrogate pairs: from the pairs I can calculate the distribution of L's. The world is in these surrogate pairs (the paurs form       the popultion). Once you have a distribution, we compare our L to the baseline of the population
          - What coordination are we capturing when we're comparing actual pairs and surrogate pairs?
          - What is left is what happens by being in the same room, tested in the same task, being together --> what we're                    interested in


--- FROM MALTE'S 2ND CLASS ---

- CRQA needs parameters: delay, raidus
     delay: The space between timeseries. Delay of 0 = no space between the three datapoints --> they're the same point! Min number is 1 then! The amount of seconds between each signal
     radius: how far datapoints are away from each other for them to be considered recurring. 
     dimension: xxx
     emb.dim: minimum is 1!
- Important that ^these parametres are the same - across conditions AND HR/Resp as well in order for us to compare

The CRQA:
- create a function: photo
- Then crqa_find(data$variable1 , data$variable2)
- We should create a new dataframe with the results --> there will be many numbers (all participants)
- Take the MEDIAN after having gotten all the params 
    Not mean because: a median is more robust towards outliers
- Preprocessing: don't replace outliers with the mean! 


Loop for baselines:
- 
```{r}
participants <- 1:10
expand.grid(p1 = "participants", p2 = "participants")

```



